Verifying Demonstrations

### 2017-08-31 properties.tex

        \item There is a mechanism that provides this property: a blockchain.
        \item There are also other structures, e.g.\ a directed 
          graph~\cite{BlockchainFreeCryptocurrencies}.
      \end{itemize}
    \end{idea}
  }
  \only<3>{%
    \begin{idea}[Created before end]
      \begin{itemize}
        \item Submit the proof to storage.
        \item The proof must've been created before it was included (duh!).
        \item If included before \(t_e\), then it was created before \(t_e\).
      \end{itemize}
    \end{idea}
  }
  \only<4>{%
    \begin{idea}[Created after start]
      \begin{itemize}
        \item Include an unpredictable value in the proof.
        \item This could be e.g.\ the hash of the \enquote{head} of the 
          \ac{tposet}, (\(t_s\) in the figure).
        \item This prevents creating proofs for future protests.
      \end{itemize}
    \end{idea}
  }
}
\end{frame}

@@

  \begin{idea}[Receipt freeness (deniability)]
    \begin{itemize}
      \item Alice submits her proof.
      \item She stores the hash of the head of the \ac{tposet}.
      \item She removes the proof and signature key.
    \end{itemize}
  \end{idea}
\end{frame}
}

\begin{frame}
\mode<presentation>{%
  \begin{idea}
    \begin{itemize}
      \item If Eve compromises Alice's device, she should not be able to use it 
        to verify that she participated.

      \item We need a signature scheme that cannot reproduce the same signature 
        when run on the same inputs.

>>>>

        \item There is a mechanism that provides this property: a blockchain.
        \item There are also other structures, e.g.\ a directed 
          graph~\cite{BlockchainFreeCryptocurrencies}.
      \end{itemize}
    \end{idea}
  }
  \only<3>{%
    \begin{idea}[Created before end]
      \begin{itemize}
        \item Submit the proof to storage.
        \item The proof must've been created before it was included.
        \item If included before \(t_e\), then it was created before \(t_e\).
      \end{itemize}
    \end{idea}
  }
  \only<4>{%
    \begin{idea}[Created after start]
      \begin{itemize}
        \item Include an unpredictable value in the proof.
        \item This could be e.g.\ the hash of the \enquote{head} of the 
          \ac{tposet}, (\(t_s\) in the figure).
        \item This prevents creating proofs for future protests.
      \end{itemize}
    \end{idea}
  }
}
\end{frame}

@@

      \item If Eve compromises Alice's device, she can use it to verify that 
        she participated.

      \item We need a signature scheme that cannot reproduce the same signature 
        when run on the same inputs.
    \end{itemize}
  \end{remark}
\end{frame}
}

\begin{frame}
\mode<presentation>{%
  \begin{idea}[Receipt freeness (deniability)]
    \begin{itemize}
      \item Alice submits her proof.
      \item She stores the hash of the head of the \ac{tposet}.
      \item She removes the proof and signature key.
